Reproducible Research in R: A Tutorial on How to Do the Same Thing More \highlighting{Than Once}

### 2021-12-01 manuscript.tex
add mdpi proof

%=================================================================
\documentclass[psych,tutorial,submit,moreauthors,pdftex]{mdpi}

@@

%% Some pieces required from the pandoc template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{4pt}}
\setlist[itemize]{leftmargin=*,labelsep=5.8mm}
\setlist[enumerate]{leftmargin=*,labelsep=4.9mm}

@@

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
\updates{yes} % If there is an update available, un-comment this line

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Reproducible Research in R: A Tutorial on how to Do the Same
Thing More Than Once}

% Authors, for the paper (add full first names)
\Author{Aaron Peikert$^{1, 2,
*}$\href{https://orcid.org/0000-0001-7813-818X}{\orcidicon}, Caspar J.
van Lissa$^{3,
4}$\href{https://orcid.org/0000-0002-0808-5024}{\orcidicon}, Andreas M.
Brandmaier$^{1, 5,
6}$\href{https://orcid.org/0000-0001-8765-6982}{\orcidicon}}

% Authors, for metadata in PDF
\AuthorNames{Aaron Peikert, Caspar J. van Lissa, Andreas M. Brandmaier}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Center for Lifespan Psychology---Max Planck Institute for
Human Development, Lentzeallee 94, 14195 Berlin, Germany; \\
$^{2}$ \quad Humboldt-Universität zu Berlin, Berlin, Germany; \\
$^{3}$ \quad Department of Methodology \& Statistics---Utrecht
University, Faculty of Social and Behavioral Sciences, Utrecht,
Netherlands; \\
$^{4}$ \quad Open Science Community Utrecht, Utrecht, Netherlands; \\
$^{5}$ \quad Max Planck UCL Centre for Computational Psychiatry and
Ageing Research Berlin, Germany, and London, UK; \\
$^{6}$ \quad MSB Medical School Berlin, Berlin, Germany; \\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:peikert@mpib-berlin.mpg.de}{\nolinkurl{peikert@mpib-berlin.mpg.de}}}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{Computational reproducibility is the ability to obtain
identical results from the \emph{same} data with the \emph{same}
computer code. It is a building block for transparent and cumulative
science because it enables the originator and other researchers, on
other computers and later in time, to reproduce and thus understand how
results came about while avoiding a variety of errors that may lead to
erroneous reporting of statistical and computational results. In this
tutorial, we demonstrate how the R package \texttt{repro} supports
researchers in creating fully computationally reproducible research
projects with tools from the software engineering community. Building
upon this notion of fully automated reproducibility we present several
applications including the preregistration of research plans with code
(Preregistration as Code, PAC). PAC eschews all ambiguity of traditional
preregistration and offers several more advantages. Making technical
advancements that serve reproducibility more widely accessible for
researchers holds the potential to innovate the research process to
become more productive, credible, and reliable.}

% Keywords
\keyword{open science; computational reproducibility; preregistration;
R; R Markdown; Make; GitHub; Docker}

@@

\captionsetup{labelformat=empty}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Scientists increasingly strive to make research data, materials, and
analysis code openly available. Sharing these digital research products
can increase scientific efficiency by enabling researchers to learn from
each other, reuse materials, and increase scientific reliability by
facilitating the review and replication of published research results.
To some extent, these potential benefits are contingent on whether these
digital research products are reproducible. Reproducibility can be
defined as the ability of anyone to obtain identical results from the
\emph{same} data with the \emph{same} computer code \citep[see][ for
details]{Peikert2019}. The credibility of empirical research results
hinges on their objectivity. Objectivity in this context means, ``in
principle it {[}the research finding{]} can be tested and understood by
anybody.'' \citep[p.~22]{popperLogicScientificDiscovery2002}. Only a
reproducible result meets these requirements. Therefore, reproducibility
has long been considered integral to empirical research. Unfortunately,
despite increasing commitment to open science practices and good will,
many projects can not yet be reproduced by other research teams
\citep{obels2020}. This is because there are various challenges to
making a research project reproducible (e.g., missing software
dependencies or ambiguous documentation of the exact computational steps
taken), and there is a lack of best practices for overcoming these
challenges \citep[but see][]{vanlissa2020worcs}. With technological
advancement, however, it is now possible to make all digital products
related to a research project available in a manner that enables
automatic reproduction of the research project with minimal effort.

With this paper, we pursue two aims. First, we want to introduce
researchers to a notion of automated reproducibility that requires no
manual steps, apart from the initial setup of the software environment.
Secondly, we discuss the implications of automated reproducibility for
changing the general approach to research. With regard to the first
goal, we discuss how to address four common threats to reproducibility,
using tools originating from software engineering \citep[see][ for
details]{Peikert2019}, and present a tutorial on how to employ these
tools to achieve automated reproducibility. A single tutorial cannot
comprehensively introduce the reader to the detail of individual tools,
but this tutorial is intended to help readers get started with a basic
workflow. The tutorial is aimed at researchers who regularly write code
to analyze their data and are willing to make relevant code, data, and
materials available, either publicly or on request. Ideally, the reader
has already created a dynamic document at some point in time (e.g., with
R Markdown or Jupyter) and used some form of version control (e.g.,
Git). The R package \texttt{repro} supports researchers in setting up
the required software and in adopting this workflow. We present
automated reproducibility as a best practice; a goal that is not always
fully achieved due to limited resources, technical restrictions, or
practical considerations, but is worth striving for nonetheless.

In pursuit of the second aim, we present a strictly reproducible and
unambiguous form of preregistration \citep{NosekRevolution2018} that
builds upon implementing this reproducible workflow, the so-called
\emph{Preregistration as Code} (PAC). PAC involves preregistering the
intended analysis code and the major part of the final scientific report
as a dynamic document, including typical sections like introduction,
methods, and results. The resulting dynamic document closely resembles
the final manuscript but uses simulated data to generate placeholder
results (e.g., figures, tables, and statistics). Simulated data serve
two functions, they allow to test the code for the planned analyses and
for preregistering the exact presentation of the results. Once the
empirical data are available, these replace the simulated data; the
results are then updated automatically, and the discussion can be
written to finalize the report.

Scientific organizations and funding bodies increasingly demand
transparent sharing of digital research products, and researchers are
increasingly willing to do so. However, although the sharing of such
digital research products is a necessary condition for reproducibility,
it is not a sufficient one. This was illustrated by an attempt to
reproduce results from open materials in the journal \emph{Cognition}
\citep{hardwicke2018}. Out of 35 published articles with open code and
data, results of 22 articles could be reproduced, but in 11 of these
cases, further assistance from the original authors was required. For 13
articles, at least 1 outcome could not be reproduced-----even with the
original authors' assistance. Another study of 62 Registered Reports
found that only 41 had data available, and 37 had analysis scripts
available \citep{obels2020}. The authors could execute only 31 of the
scripts without error and reproduce the results of only 21 articles
(within a reasonable time). These failed attempts to reproduce findings
highlight the need for widely accepted reproducibility standards because
open repositories do not routinely provide sufficient information to
reproduce relevant computational and statistical results. If digital
research products are available but not reproducible, their added value
is limited.

@@

We have structured the tutorial with a \emph{learning-by-doing} approach
in mind, such that readers can follow along on their own computers. We
explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the
statistical programming language R \citep[tested with version
4.0.4]{R-base}.

\hypertarget{threats-to-reproducibility-and-appropriate-remedies}{%
\section{Threats to Reproducibility and Appropriate
Remedies}\label{threats-to-reproducibility-and-appropriate-remedies}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \emph{Multiple inconsistent versions of code, data, or both}; for
  example, the data set may have changed over time because outliers were
  removed at a later stage or an item was later recoded; or, the
  analysis code may have been modified during the writing of a paper
  because a bug was removed at some point in time. It may then be
  unclear which version of code and data was used to produce some
  reported set of results.
\item
  \emph{Copy-and-paste errors}; for example, results are often manually
  copied from a statistical computing language into a text processor; if
  a given analysis is re-run and results are manually updated in the
  text processor, this may inadvertently lead to inconsistencies between
  the reported result and the reproduced result.
\item
  \emph{Undocumented or ambiguous order of computation}; for example,
  with multiple data and code files, it may be unclear which scripts
  should be executed in what order; or, some of the computational steps
  are documented (e.g., final analysis), but other steps were conducted
  manually without documentation (e.g., executing a command manually
  rather than in a script; copy-and-pasting results from one program to
  another).
\item
  \emph{Ambiguous software dependencies}; for example, a given analysis
  may depend on a specific version of a specific software package, or
  rely on software that might not be available on a different computer,
  or no longer exist at all; or a different version of the same software
  may produce different results.
\end{enumerate}

We have developed a workflow that achieves long-term and cross-platform
computational reproducibility of scientific data analyses. It leverages
established tools and practices from software engineering and rests on
four pillars that address the aforementioned causes of
non-reproducibility \citep{Peikert2019}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Version control
\item
  Dynamic document generation
\item
  Dependency tracking
\item
  Software management
\end{enumerate}

The remainder of this section briefly explains why each of these four
building blocks is needed and details their role in ensuring
reproducibility. A more extensive treatment of these tools is given in
\citet{Peikert2019}.

@@

\texttt{Git} tracks changes to all project-related files (e.g.,
materials, data, and code) over time. At any stage, individual files or
the entire project can be compared to, or reverted to, an earlier
version. Moreover, contributions (e.g., from collaborators) can be
compared to, and incorporated in the main version of the project.
Version control thus reduces the risk of losing work and facilitates
collaboration. \texttt{Git} is built around snapshots that represent the
project state at a given point in time. These snapshots are called
\emph{commits} and work like a ``save'' action. Ideally, each commit has
a message that succinctly describes these changes. It is good practice
to make commits for concrete milestones (e.g., ``Commented on
Introduction,'' ``Added SES as a covariate,'' ``Address Reviewer 2's
comment 3''). This makes it easier to revert specific changes than when
multiple milestones are joined in one commit, e.g., ``Changes made on
19/07/2021''. Each commit refers back to its ancestor, and all commits
are thus linked in a timeline. The entirety of commits (i.e., the
version-controlled project) is called a repository. In \texttt{Git},
specific snapshots of a repository can be tagged, such that the user can
clearly label which version of the project was used to create a
preregistration, preprint, or final version of the manuscript as
accepted by a journal. \texttt{Git} has additional features beyond basic
version control, such as ``branches'' (parallel versions of a project
that can later be merged again) to facilitate simultaneous
collaboration. \citet{vuorreCuratingResearchAssets2018} provide a more
extensive treatment of how \texttt{Git} functions and how to use
\texttt{Git} for research. \citet{bryanExcuseMeYou2018} provides
additional information on how to track \texttt{R\ Markdown} documents.
Collaborating via \texttt{Git} is facilitated by uploading the
repository to a cloud-based service. We recommend GitHub as a host for
\texttt{Git} repositories because of its popularity among R users.
GitHub has many tools that facilitate working with \texttt{Git} --- in
particular project management and collaboration --- but these are not
central to achieving reproducibility.

@@

Dynamic document generation integrates both steps. Through dynamic
document generation, code becomes an integral, although usually hidden,
part of the manuscript, complementing the verbal description and
allowing interested readers to gain a deeper understanding of the
contents
\citep{knuthCWEBSystemStructured, claerboutElectronicDocumentsGive1992}.
\texttt{R\ Markdown} uses \texttt{Markdown} for text formatting and R
(or other programming languages) for writing the statistical analysis.
\texttt{Markdown} is a lightweight text format in plain text with a
minimal set of reserved symbols for formatting instructions. This way,
\texttt{Markdown} does not need any specialized software for editing. It
is userfriendly (unlike, for example, \texttt{LaTeX}
\citep{lamportLATEXDocumentPreparation1994}), works well with version
control systems, and can be exported to various document formats, such
as HTML websites, a Microsoft Word document, a typeset PDF file (for
example, via LaTeX journal templates), or a Powerpoint presentation.
\texttt{Markdown} can be used for all sorts of academic documents,
ranging from simple sketches of ideas to scientific manuscripts
\citep{R-rticles} and presentations \citep{revealjs}, or even résumés
\citep{vitae}. \texttt{R\ Markdown} extends regular \texttt{Markdown} by
allowing users to include R code chunks (in fact, arbitrary computer
code \citep[Chapter 15, Chapter 15, Other
Languages]{xieMarkdownCookbook2020}) into a \texttt{Markdown} document.
Upon rendering the document, the code blocks are executed, and their
output is dynamically inserted into the document. This allows the
creation of (conditionally) formatted text, statistical results, and
figures that are guaranteed to be up-to-date because they are created
anew every time the document is rendered to its output format (e.g.,
presentation slides or a journal article).
\citet{xieMarkdownCookbook2020} provides an extensive yet practical
introduction to most features of \texttt{R\ Markdown}.

@@

\emph{Dependency tracking} helps automatically resolve dependencies
between project files. In essence, researchers provide a collection of
\emph{computational recipes}. A computational recipe describes how
inputs are processed to deterministically create a specific output in a
way that is automatically executable. The concept of computational
recipes is central to our understanding of reproducibility because it
enables a unified way to reproduce a project automatically. Similar to a
collection of cooking recipes, we can have multiple products
(\emph{targets}) with different ingredients (\emph{requirements}) and
different steps of preparation (\emph{recipes}). In the context of
scientific data analysis, targets are typically the final scientific
report (e.g., the one to be submitted to a journal) and possibly
intermediate results (such as preprocessed data files, simulation
results, and analysis results). A workflow that involves renaming
variable names by hand in a graphical spreadsheet application, for
example, is therefore incompatible with automated reproducibility.
Another property of a computational recipe is that the same inputs
should always result in the same outputs. For most computer code (given
the same software is used), this property is fulfilled. However, one
noteworthy exception is the generation of pseudo-random numbers.
Whenever random numbers are used in a computation, it is only
reproducible if the random number generator generates the same numbers.
To ensure identical random numbers, users may fix the state of the
random number generated with a so-called seed (e.g.~\texttt{set.seed()}
in R), but they also need to guarantee that the pseudo-random number
generator is unchanged \citep[see][]{Peikert2019}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{manuscript.pdf:}\NormalTok{ manuscript.Rmd simulated\_data.csv}
  \ExtensionTok{Rscript} \AttributeTok{{-}e} \StringTok{\textquotesingle{}rmarkdown::render("manuscript.Rmd")\textquotesingle{}}

\ExtensionTok{simulated\_data.csv:}\NormalTok{ simulate.R}
  \ExtensionTok{Rscript} \AttributeTok{{-}e} \StringTok{\textquotesingle{}source("simulate.R")\textquotesingle{}}
\end{Highlighting}
\end{Shaded}

There are two targets, the final rendered report
(\texttt{manuscript.pdf}, l. 1) and the simulation results
(\texttt{simulation\_results.csv}, l. 4). Each target is followed by a
colon and a list of requirements. If a requirement is newer than the
target, the recipe will be executed to rebuild the target. If a
requirement does not exist, \texttt{Make} uses a recipe to build the
requirement before building the target. Here, if one were to build the
final \texttt{manuscript.pdf} by rendering the \texttt{R\ Markdown} with
the command shown in l.2, \texttt{Make} would check whether the file
\texttt{simulation\_results.csv} exists; if not, it would issue the
command in l.5 to run the simulation before rendering the manuscript.
This ensures that the simulated data are present before the manuscript
is built, and that the simulation is re-run and the manuscript is
rebuilt if the simulation code was changed. \texttt{Make} therefore
offers a standardized process to reproduce projects, regardless of the
complexity or configuration of the project. Note that the Workflow for
Open Reproducible Code in Science (WORCS) we presented elsewhere
\citep{vanlissa2020worcs} does not explicitly contain this dependency
tracking element, but its strict structure of only containing one
definite \texttt{R\ Markdown} still makes dependencies between files
unambiguous.

A version-controlled dynamic document with dependency tracking still
relies on external software. Troubleshooting issues specific to a
particular programming language or dependent tool typically require
considerable expertise and threaten reproducibility. \emph{Software
management} refers to the act of providing records of, or access to, all
software packages and system libraries a project depends on. One
comprehensive approach to software management is containerization. The
central idea is that by ``{[}..{]} packaging the key elements of the
computational environment needed to run the desired software {[}makes{]}
the software much easier to use, and the results easier to reproduce
{[}\ldots{]}'' \citep[p.~174]{silverSoftwareSimplified2017}.

>>>>

%=================================================================
\documentclass[psych,tutorial,accept,moreauthors,pdftex]{Definitions/mdpi}

@@

%% Some pieces required from the pandoc template
%\providecommand{%\tightlist}{%
 % \setlength{\itemsep}{0pt}\setlength{\parskip}{4pt}}
%\setlist[itemize]{leftmargin=*,labelsep=5.8mm}
%\setlist[enumerate]{leftmargin=*,labelsep=4.9mm}

@@

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
\externaleditor{Academic Editor: {Alexander Robitzsch}} %MDPI: Please add the academic editor.
\datereceived{} 
\dateaccepted{} 
\datepublished{}
\hreflink{https://doi.org/} % If needed use \linebreak

@@

%=================================================================
% Full title of the paper (Capitalized)
\Title{Reproducible Research in R: A Tutorial on How to Do the Same
Thing More \highlighting{Than Once}} %MDPI: the article type in the document is different with that in Susy, please confirm.

\TitleCitation{Reproducible Research in R: A Tutorial on How to Do the Same
Thing More Than Once}

% Authors, for the paper (add full first names)
\Author{\highlighting{Aaron Peikert~$^{1,2,*}$\href{https://orcid.org/0000-0001-7813-818X}{\orcidicon}} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading.
, \highlighting{Caspar J. van Lissa~$^{3,4}$\href{https://orcid.org/0000-0002-0808-5024}{\orcidicon}} %MDPI: This author is different from susy. Please check.
 and Andreas M. Brandmaier~$^{1,5,6}$\href{https://orcid.org/0000-0001-8765-6982}{\orcidicon}}

% Authors, for metadata in PDF
\AuthorNames{Aaron Peikert, Caspar J. van Lissa and Andreas M. Brandmaier}

\AuthorCitation{Peikert, A.;  van Lissa, J.; Brandmaier, A.M.}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, \mbox{14195 Berlin, Germany;} brandmaier@mpib-berlin.mpg.de\\
$^{2}$ \quad Humboldt-Universität zu Berlin, \hl{Berlin}, Germany\\%MDPI: Please add the post code.
$^{3}$ \quad \hl{Department} of Methodology \& Statistics---Utrecht \hl{University}, \hl{Faculty} of Social and Behavioral Sciences%MDPI: Please check the address order.  (order guide: Center / Laboratory / Group / Programme / Unit < Department / Division / Faculty / Campus / Institute / School < College / University / Universiti)
, \hl{Utrecht}, The Netherlands; C.J.vanLissa@uu.nl\\
$^{4}$ \quad Open Science Community Utrecht, \hl{Utrecht}, The Netherlands\\
$^{5}$ \quad Max Planck UCL Centre for Computational Psychiatry and Ageing Research, \mbox{\hl{Berlin, Germany, and London, UK}} %MDPI: 1. Please check if there are two separator affiliations. If so, please split them. 2. Please add the post code.
\\
$^{6}$ \quad MSB Medical School Berlin, \hl{Berlin}, Germany}

% Contact information of the corresponding author
\corres{Correspondence: peikert@mpib-berlin.mpg.de}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{Computational reproducibility is the ability to obtain
identical results from the \emph{same} data with the \emph{same}
computer code. It is a building block for transparent and cumulative
science because it enables the originator and other researchers, on
other computers and later in time, to reproduce and thus understand how
results came about, while avoiding a variety of errors that may lead to
erroneous reporting of statistical and computational results. In this
tutorial, we demonstrate how the R package \texttt{repro} supports
researchers in creating fully computationally reproducible research
projects with tools from the software engineering community. Building
upon this notion of fully automated reproducibility, we present several
applications including the preregistration of research plans with code
(Preregistration as Code, PAC). PAC eschews all ambiguity of traditional
preregistration and offers several more advantages. Making technical
advancements that serve reproducibility more widely accessible for
researchers holds the potential to innovate the research process and to
help it become more productive, credible, and reliable.}

% Keywords
\keyword{open science; computational reproducibility; preregistration;
R; R Markdown; make; GitHub; docker}%MDPI: 1. The upper case has been removed. Please confirm. 2. Please check if R is duplicated here.

@@

%\captionsetup{labelformat=empty}

%\hypertarget{introduction}
\section{Introduction}\label{introduction}

Scientists increasingly strive to make research data, materials, and
analysis code openly available. Sharing these digital research products
can increase scientific efficiency by enabling researchers to learn from
each other, reuse materials, and increase scientific reliability by
facilitating the review and replication of published research results.
To some extent, these potential benefits are contingent on whether these
digital research products are reproducible. Reproducibility can be
defined as the ability of anyone to obtain identical results from the
\emph{same} data with the \hl{\emph{same}} %MDPI: Is the italic necessary? Can it be deleted?
 computer code (see~\citep{Peikert2019} \hl{for
details).} %MDPI: The structure of reference citation has been changed. So as the follows. Please confirm.
 The credibility of empirical research results
hinges on their objectivity. Objectivity in this context means, ``in
principle it {[}the research finding{]} can be tested and understood by
anybody.'' (\citep{popperLogicScientificDiscovery2002} p.~22). Only a
reproducible result meets these requirements. Therefore, reproducibility
has long been considered integral to empirical research. Unfortunately,
despite increasing commitment to open science practices and good will,
many projects can not yet be reproduced by other research teams
\citep{obels2020}. This is because there are various challenges to
making a research project reproducible (e.g., missing software
dependencies or ambiguous documentation of the exact computational steps
taken), and there is a lack of best practices for overcoming these
challenges (but see~\citep{vanlissa2020worcs}). With technological
advancement, however, it is now possible to make all digital products
related to a research project available in a manner that enables
automatic reproduction of the research project with minimal effort.

With this paper, we pursue two aims. First, we want to introduce
researchers to a notion of automated reproducibility that requires no
manual steps, apart from the initial setup of the software environment.
Secondly, we discuss the implications of automated reproducibility for
changing the general approach to research. With regard to the first
goal, we discuss how to address four common threats to reproducibility,
using tools originating from software engineering (see~\citep{Peikert2019} for
details), and present a tutorial on how to employ these
tools to achieve automated reproducibility. A single tutorial cannot
comprehensively introduce the reader to the detail of individual tools,
but this tutorial is intended to help readers get started with a basic
workflow. The tutorial is aimed at researchers who regularly write code
to analyze their data and are willing to make relevant code, data, and
materials available, either publicly or on request. Ideally, the reader
has already created a dynamic document at some point in time (e.g., with
R Markdown or Jupyter) and used some form of version control (e.g.,
Git). The R package \texttt{repro} supports researchers in setting up
the required software and in adopting this workflow. We present
automated reproducibility as a best practice; a goal that is not always
fully achieved due to limited resources, technical restrictions, or
practical considerations, but is worth striving for nonetheless.

In pursuit of the second aim, we present a strictly reproducible and
unambiguous form of preregistration~\citep{NosekRevolution2018} that
builds upon implementing this reproducible workflow, the so-called
\emph{Preregistration as Code} (PAC). PAC involves preregistering the
intended analysis code and the major part of the final scientific report
as a dynamic document, including typical sections like introduction,
methods, and results. The resulting dynamic document closely resembles
the final manuscript but uses simulated data to generate placeholder
results (e.g., figures, tables, and statistics). Simulated data serve
two functions, they allow to test the code for the planned analyses and
for preregistering the exact presentation of the results. Once the
empirical data are available, these replace the simulated data; the
results are then updated automatically, and the discussion can be
written to finalize the report.

Scientific organizations and funding bodies increasingly demand
transparent sharing of digital research products, and researchers are
increasingly willing to do so. However, although the sharing of such
digital research products is a necessary condition for reproducibility,
it is not a sufficient one. This was illustrated by an attempt to
reproduce results from open materials in the journal \emph{Cognition}
\citep{hardwicke2018}. Out of 35 published articles with open code and
data, the results of 22 articles could be reproduced, but further assistance from the original authors was required in 11 of these cases. For 13
articles, at least one outcome could not be reproduced---even with the
original authors' assistance. Another study of 62 registered reports
found that only 41 had data available, and 37 had analysis scripts
available~\citep{obels2020}. The authors could execute only 31 of the
scripts without error and reproduce the results of only 21 articles
(within a reasonable time). These failed attempts to reproduce findings
highlight the need for widely accepted reproducibility standards because
open repositories do not routinely provide sufficient information to
reproduce relevant computational and statistical results. If digital
research products are available but not reproducible, their added value
is~limited.

@@

We have structured the tutorial with a \emph{learning-by-doing} approach
in mind, such that readers can follow along on their own computers. We
explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the
statistical programming language R (\citep{R-base} tested with version
4.0.4).

%\hypertarget{threats-to-reproducibility-and-appropriate-remedies}
\section{Threats to Reproducibility and Appropriate
Remedies}\label{threats-to-reproducibility-and-appropriate-remedies}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  \highlighting{\emph{Multiple inconsistent versions of code, data, or both};} %MDPI: Is the italic necessary? Can it be deleted?
 for
  example, the data set may have changed over time because outliers were
  removed at a later stage or an item was later recoded; or, the
  analysis code may have been modified during the writing of a paper
  because a bug was removed at some point in time. It may then be
  unclear which version of code and data was used to produce some
  reported set of results.
\item
  \highlighting{\emph{Copy-and-paste errors};} for example, results are often manually
  copied from a statistical computing language into a text processor; if
  a given analysis is re-run and results are manually updated in the
  text processor, this may inadvertently lead to inconsistencies between
  the reported result and the reproduced result.
\item
  \highlighting{\emph{Undocumented or ambiguous order of computation};} for example,
  with multiple data and code files, it may be unclear which scripts
  should be executed in what order; or, some of the computational steps
  are documented (e.g., final analysis), but other steps were conducted
  manually without documentation (e.g., executing a command manually
  rather than in a script; copy-and-pasting results from one program to
  another).
\item
  \highlighting{\emph{Ambiguous software dependencies};} for example, a given analysis
  may depend on a specific version of a specific software package, or
  rely on software that might not be available on a different computer,
  or no longer exist at all; or a different version of the same software
  may produce different results.
\end{enumerate}

We have developed a workflow that achieves long-term and cross-platform
computational reproducibility of scientific data analyses. It leverages
established tools and practices from software engineering and rests on
four pillars that address the aforementioned causes of
non-reproducibility~\citep{Peikert2019}:

\begin{enumerate}
%\def\labelenumi{\arabic{enumi}.}
%%\tightlist
\item  Version control
\item  Dynamic document generation
\item  Dependency tracking
\item  Software management
\end{enumerate}

The remainder of this section briefly explains why each of these four
building blocks is needed and details their role in ensuring
reproducibility. A more extensive treatment of these tools is given in
Peikert and Brandmaier~\citep{Peikert2019}.

@@

\texttt{Git} tracks changes to all project-related files (e.g.,
materials, data, and code) over time. At any stage, individual files or
the entire project can be compared to, or reverted to, an earlier
version. Moreover, contributions (e.g., from collaborators) can be
compared to and incorporated in the main version of the project.
Version control thus reduces the risk of losing work and facilitates
collaboration. \texttt{Git} is built around snapshots that represent the
project state at a given point in time. These snapshots are called
\emph{commits} and work like a ``save'' action. Ideally, each commit has
a message that succinctly describes these changes. It is good practice
to make commits for concrete milestones (e.g., ``Commented on
Introduction,'' ``Added SES as a covariate,'' ``Address Reviewer 2's
comment 3''). This makes it easier to revert specific changes than when
multiple milestones are joined in one commit, e.g., ``Changes made on
19/07/2021''. Each commit refers back to its ancestor, and all commits
are thus linked in a timeline. The entirety of commits (i.e., the
version-controlled project) is called a repository. In \texttt{Git},
specific snapshots of a repository can be tagged, such that the user can
clearly label which version of the project was used to create a
preregistration, preprint, or final version of the manuscript as
accepted by a journal. \texttt{Git} has additional features beyond basic
version control, such as ``branches'' (parallel versions of a project
that can later be merged again) to facilitate simultaneous
collaboration. Vuorre and Curley~\citep{vuorreCuratingResearchAssets2018} provide a more
extensive treatment of how \texttt{Git} functions and how to use
\texttt{Git} for research. Bryan~\citep{bryanExcuseMeYou2018} provides
additional information on how to track \texttt{R\ Markdown} documents.
Collaborating via \texttt{Git} is facilitated by uploading the
repository to a cloud-based service. We recommend GitHub as a host for
\texttt{Git} repositories because of its popularity among R users.
GitHub has many tools that facilitate working with \texttt{Git}---
particularly in project management and collaboration---but these are not
central to achieving reproducibility.

@@

Dynamic document generation integrates both steps. Through dynamic
document generation, code becomes an integral, although usually hidden,
part of the manuscript, complementing the verbal description and
allowing interested readers to gain a deeper understanding of the
contents
\citep{knuthCWEBSystemStructured, claerboutElectronicDocumentsGive1992}.
\texttt{R\ Markdown} uses \texttt{Markdown} for text formatting and R
(or other programming languages) for writing the statistical analysis.
\texttt{Markdown} is a lightweight text format in plain text with a
minimal set of reserved symbols for formatting instructions. This way,
\texttt{Markdown} does not need any specialized software for editing. It
is userfriendly (unlike, for example, \texttt{LaTeX}
\citep{lamportLATEXDocumentPreparation1994}), works well with version
control systems, and can be exported to various document formats, such
as HTML websites, a Microsoft Word document, a typeset PDF file (for
example, via LaTeX journal templates), or a Powerpoint presentation.
\texttt{Markdown} can be used for all sorts of academic documents,
ranging from simple sketches of ideas to scientific manuscripts
\citep{R-rticles} and presentations~\citep{revealjs}, or even résumés
\citep{vitae}. \texttt{R\ Markdown} extends regular \texttt{Markdown} by
allowing users to include R code chunks (in fact, arbitrary computer
code \citep[Chapter 15, Chapter 15, Other
Languages]{xieMarkdownCookbook2020}) into a \texttt{Markdown} document.
Upon rendering the document, the code blocks are executed, and their
output is dynamically inserted into the document. This allows the
creation of (conditionally) formatted text, statistical results, and
figures that are guaranteed to be up-to-date because they are created
anew every time the document is rendered to its output format (e.g.,
presentation slides or a journal article).
Xie et al.~\citep{xieMarkdownCookbook2020} provides an extensive yet practical
introduction to most features of \texttt{R\ Markdown}.

@@

\emph{Dependency tracking} helps automatically resolve dependencies
between project files. In essence, researchers provide a collection of
\emph{computational recipes}. A computational recipe describes how
inputs are processed to deterministically create a specific output in a
way that is automatically executable. The concept of computational
recipes is central to our understanding of reproducibility because it
enables a unified way to reproduce a project automatically. Similar to a
collection of cooking recipes, we can have multiple products
(\emph{targets}) with different ingredients (\emph{requirements}) and
different steps of preparation (\emph{recipes}). In the context of
scientific data analysis, targets are typically the final scientific
report (e.g., the one to be submitted to a journal) and produce possibly
intermediate %pls check (such as preprocessed data files, simulation
results, and analysis results). A workflow that involves renaming
variable names by hand in a graphical spreadsheet application, for
example, is therefore incompatible with automated reproducibility.
Another property of a computational recipe is that the same inputs
should always result in the same outputs. For most computer code (given
the same software is used), this property is fulfilled. However, one
noteworthy exception is the generation of pseudo-random numbers.
Whenever random numbers are used in a computation, it is only
reproducible if the random number generator generates the same numbers.
To ensure identical random numbers, users may fix the state of the
random number generated with a so-called seed (e.g.~\texttt{set.seed()}
in R), but they also need to guarantee that the pseudo-random number
generator is unchanged~(see~\citep{Peikert2019}).

@@

\begin{adjustwidth}{0.5cm}{0cm} 
\begin{Shaded}
\begin{Highlighting}[]
\ExtensionTok{manuscript.pdf:}\NormalTok{ manuscript.Rmd simulated\_data.csv}
  \ExtensionTok{Rscript} \AttributeTok{{-}e} \StringTok{\textquotesingle{}rmarkdown::render("manuscript.Rmd")\textquotesingle{}}

\ExtensionTok{simulated\_data.csv:}\NormalTok{ simulate.R}
  \ExtensionTok{Rscript} \AttributeTok{{-}e} \StringTok{\textquotesingle{}source("simulate.R")\textquotesingle{}}
\end{Highlighting}
\end{Shaded}
\end{adjustwidth}

%%\begin{figure*}[H]
%\begin{Shaded}
%%\begin{Highlighting}[]
%\noindent\ExtensionTok{\texttt{manuscript.pdf:}}\NormalTok{\texttt{ manuscript.Rmd simulated\_data.csv}}\\[-2ex]
%
%\ExtensionTok{\texttt{Rscript}} \AttributeTok{\texttt{{-}e}} \StringTok{\texttt{\textquotesingle{}rmarkdown::render("manuscript.Rmd")\textquotesingle{}}}\\
%
%\noindent\ExtensionTok{\texttt{simulated\_data.csv:}}\NormalTok{\texttt{ simulate.R}}\\[-2ex]
%
%\ExtensionTok{\texttt{Rscript}} \AttributeTok{\texttt{{-}e}} \StringTok{\texttt{\textquotesingle{}source("simulate.R")\textquotesingle{}}}
%%\end{Highlighting}
%\end{Shaded}
%%\end{figure*}
